Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-09 paper/main.tex
backing up changes...
working on methods section:   - added descriptions of temporal clustering and SPC analyses

\paragraph*{Clustering scores and memory fingerprints.}

@@

@@

\subsubsection{Serial position curve}

>>>>

\paragraph*{Clustering scores (uncorrected).}

\paragraph*{Permutation-corrected clustering scores.}

\paragraph*{Memory fingerprints.}

@@

Temporal clustering describes a participant's tendency to organize their recall
sequences by the learned items' encoding positions. For instance, if a
participant recalled the episode events in the exact order they occurred (or in
exact reverse order), this would yield a score of 1. If a participant recalled
the events in random order, this would yield an expected score of 0.5. For each
recall-event transition (and separately for each participant), we sorted all
not-yet-recalled events according to their absolute lag (that is, distance away
in the episode). We then computed the percentile rank of the next event the
participant recalled. We took an average of these percentile ranks across all
of the participant’s recalls to obtain a single (uncorrected) temporal clustering score for
the participant.  Finally, as with the feature-based clustering scores, we applied
our permutation correction procedure to obtain a corrected clustering score.

@@

\subsubsection*{Serial position curve}

Serial position curves~\citep{Murd62a} reflect the proportion of participants
who remember each item as a function of the item’s serial position during
encoding. For each participant, we initialized a number-of-lists (16) by number-of-words-per-list
(16) matrix of zeros. Then, for each correct recall, we identified the
presentation position of the word and entered a 1 into that position (row:
list; column: presentation position) in the matrix. This resulted in a matrix
whose entries indicated whether or not the words presented at each position, on
each list, were recalled by the participant (depending on whether the
corresponding entires were set to one or zero). Finally, we averaged over the
rows of the matrix to yield a 1 by 16 array representing the proportion of
words at each position that the participant remembered.
